### 2013-09-03 main.tex
slight fixes to layout
slight rewrite of acknoledgements

\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{scrbook}

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
\usepackage{xspace}
\usepackage{setspace}

@@

\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE On Learning Structured Prediction For Semantic Segmentation}}
\par
\vspace{1.5in} {\large Andreas Christian M\"uller}
\par \vspace{0.5in}
Abteilung VI, Autonomie Intelligente Systeme \par
Institut f\"ur Informatik
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

\tableofcontents

%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
\chapter*{Abstract}

@@

During my work on this dissertation, my ideas were shaped by many of my fellow
students and researchers. First and foremost I am in debt to Hannes Schulz,
whose feedback proved to be invaluable during my studies.
I would like to thank Christoph Lampert, for hosting me as a visiting researcher
at the IST Austria. His guidance and advice helped me in directing my further
research. My thanks are also extended to Sebastian Nowozin for his collaboration,
many helpful discussions, and advise.

@@

I have been lucky to be a part of the scikit-learn community, whose developers
have been a constant source of encouragement and feedback to me. My understanding
of machine learning as well as software engineering has been greatly affected
by the constant exchange with Olivier Grisel, Lars Buitinck, Gael Varoquax,
Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and others.

I also thank my parents and my sister for their continuing support.

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
\usepackage{xspace}
\onehalfspacing
\KOMAoptions{DIV=last}

@@

\begin{spacing}{1}
\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE On Learning Structured Prediction For Semantic Segmentation}}
\par
\vspace{1.5in} {\large Andreas Christian M\"uller}
\par \vspace{0.5in}
Abteilung VI, Autonomie Intelligente Systeme \par
Institut f\"ur Informatik
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

\tableofcontents
\end{spacing}
%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
\chapter*{Abstract}

@@

During my work on this dissertation, my ideas were shaped by many of my fellow
students and researchers. First and foremost I am in debt to Hannes Schulz,
whose feedback proved to be invaluable during my studies.
I would like to thank Christoph Lampert for hosting me as a visiting researcher
at the IST Austria. His guidance and advice helped me in directing my further
research. My thanks are also extended to Sebastian Nowozin for his collaboration,
many helpful discussions, and advise.

@@

I have been lucky to be a part of the scikit-learn community, whose developers
have been a constant source of encouragement and inspiration to me. My
understanding of machine learning as well as software engineering has been
greatly affected by the continuing exchange with Olivier Grisel, Lars Buitinck,
Gael Varoquax, Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and
others.

I also thank my parents and my sister for their support.
